Open Science, Open Plant Pathology

### 2020-04-22 analysis/paper/paper.Rmd
Add more to methods on software used and add table of software used

@@

A custom R function, `Reproducibility.in.Plant.Pathology::import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2020].

@@

>>>>

Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
When working with these data in R, all strings of software character values were converted to fully uppercase to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
A custom R function, `Reproducibility.in.Plant.Pathology::import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2020].

@@

Software citations were also reasonably well reported in the literature with 120 scoring "2" where the main software was cited with version numbers and 57 scoring "3" where full citations including R packages or the SAS PROC used were cited where appropriate (Table \@ref(tab:sc)).

The most frequently cited software was SAS.
The remainder were mostly specialised softwares with the exception of Microsoft Excel, tied for 8th.

@@

```{r software_cite, echo=FALSE, message=FALSE, warning=FALSE}
import_notes() %>%
  tabyl(software_cite) %>%
  select(-percent) %>% 
  rename(`software citation` = software_cite,
         percent = valid_percent) %>% 
  flextable() %>%
  set_caption(
    "Table: (\\#tab:sc) Article ratings for software citations where '0', not specified or mentioned in publication to '3', fully cited with proper version numbers and all procedures detailed."
  ) %>% 
  autofit()
```

```{r software_used, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyr)

rrpp_software <-
  import_notes() %>%
  transform(software_used = strsplit(software_used, ",")) %>%
  unnest(software_used) %>% 
  mutate(software_used = trimws(software_used)) %>% 
  mutate(software_used = toupper(software_used)) # convert all to uppercase to standardise

rrpp_software %>% 
  tabyl(software_used) %>%
  select(c(-percent, -valid_percent)) %>% 
  rename(`software used` = software_used) %>% 
  arrange(-n) %>% 
  slice(seq_len(14)) %>% 
  drop_na() %>% 
  flextable() %>%
  set_caption(
    "Table: (\\#tab:su) Top 10 softwares cited in all articles. Software used is any software package mentioned by name or properly cited in the evaluated articles, n is the number of times it was mentioned. All software names were converted to fully upper-case letters to avoid any inter-evaluator data entry issues."
  ) %>% 
  autofit()
```
